sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-23 doc/paper.Rmd
Adjust table

```{r compare-table}
library(kableExtra)
suppressMessages(suppressWarnings(d <- readr::read_csv(here::here("doc/software-comparison.csv"), show_col_types = FALSE)))
d <- t(d)
d <- cbind(row.names(d), d)
d[d == "1"] <- "\\checkmark"
d[d == "1*"] <- "\\checkmark\\footnote{a}"
d[d == "0"] <- "--"
d[d == "0*"] <- "--\\footnote{a}"
d <- as.data.frame(d)
names(d) <- d[1,]
d <- d[-1,]
names(d)[1] <- ""
row.names(d) <- NULL
d <- d[,c(1, 2, 3, 5, 6, 4)]
d <- d[!grepl("SPDE", d[,1]), ]
knitr::kable(d, format = "latex", caption = "Title of the table", 
  booktabs = TRUE, linesep = "", escape = FALSE, row.names = FALSE) %>%
  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::footnote(
    number = c("Footnote 1; ", "Footnote 2; ")
  )
```

>>>>

```{r compare-table}
library(kableExtra)
suppressMessages(suppressWarnings(d <- readr::read_csv(here::here("doc/software-comparison.csv"), show_col_types = FALSE)))
d <- as.matrix(d)
d[d == "1"] <- "\\checkmark"
d[d == "1*"] <- "\\checkmark\\footnote{a}"
d[d == "0"] <- "--"
d[d == "0*"] <- "--\\footnote{a}"
d <- as.data.frame(d)
names(d)[1] <- ""
row.names(d) <- NULL
d <- d[,c(1, 2, 3, 5, 6, 4)]
d <- d[!grepl("SPDE", d[,1]), ]
knitr::kable(d, format = "latex", caption = "Title of the table", 
  booktabs = TRUE, linesep = "", escape = FALSE, row.names = FALSE) %>%
  kableExtra::kable_styling(font_size = 8) %>% 
  kableExtra::footnote(
    number = c("Footnote 1; ", "Footnote 2; ")
  )
```
